Insert the article title here

### 2018-03-28 writeup/manuscript.tex
Update manuscript.tex

\author{%%%% Author details
Alasdair D. F. Clarke$^1$, Jess Irons$^2$, Warren James$^3$, Andrew Leber$^2$ and Amelia R Hunt$^3$}

@@

@@

@@

Following \cite{irons-leber2016}, individual differences will be characterized using two measures:\\
1) Proportion of optimal choices on plateaus. An optimal choice is defined as responding to whichever of the two target colours has the fewest items in the display. This will be based on correct plateau trials only. \\ 
2) Switching frequency. Switching is defined as responding to a different target color on trial $N$+1 than on trial $N$, and is presented as a proportion of the total number of trials (excluded incorrect trials, the trial after an incorrect trial, and the first trial of each block).\\
Both measures have been shown to correlate with overall RT in previous experiments (Proportion Optimal $r$=-.56, $p$<.001; Switch Frequency $r$=.45, $p$=.001; based on $N$=50 and using the same number of trials as in the current experiment). As additional validation, correlational analyses between both measures and RT will also be conducted in the current experiment.

@@

Data analysis will follow \cite{kristjansson2014} and Johannesson et al. (2016). The main measure of interest will be the average run length per trial. A run is defined as a succession of one or more of the same target type which is followed and preceded by the other target type or no target. The average length is the average number of consecutive target selections per run. As with the other experiments, we will also measure the average response (time to select the final target on correct trials).

>>>>

\author{%%%% Author details
Alasdair D. F. Clarke$^1$, Jessica L Irons$^2$, Warren James$^3$, Andrew B Leber$^2$ and Amelia R Hunt$^3$}

@@

\subsubsection{Adaptive Choice Visual Search}

The ACVS was based on the task described in Irons & Leber (2016), with a few changes [Or identical to the task described in Experiment 1 of Irons & Leber, in press by then hopefully].

Each search display was composed of 54 small squares (size? What was viewing distance & screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The inner ring was XX° and the outer ring was XX° from fixation. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”. Variable distractors changes colors afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change color from almost red to magenta (at the 4th trial in the transition) to almost blue (see Irons & Leber, 2017, for the specific color values? Or supplemental?). The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red. This 24-trial cycle would repeat throughout the entire experiment.

A white digit appeared inside each square. Two targets – a red square and a blue square each with a digit between 2 and 5 – were embedded in every search display. The two target digits were always different, to enable us to distinguish the chosen target. The remaining red, blue and variable squares all contained digits between 6–9. Green squares could contain any digit between 2-9. The location of the targets and distractor within the search display were randomized on each trial.

Participants were informed that the search displays would contain two targets on every trial, that they need only find one target on each trial and that they were always free to search for either one. A trial began with a 1.5s ITI containing a central fixation cross, followed by the search display until a response was made. Participant responded by pressing a key that corresponded to the digit inside the target (V, B, N and M keys corresponding to 2, 3, 4 and 5 respectively). Participants completed 10 practice trials, followed by 3 blocks of 96 trials. Each block started on a red plateau.

@@

The foraging task was based on Kristjansson, Johannesson & Thornton (2014) and Johannsesson et al (2016). Participants completed the feature foraging and conjunction foraging tasks on separate days, with the order counterbalanced (was it counterbalanced?).

In the feature foraging task, search displays contained 80 small circles (size), 20 red (RGB: 180, 0, 0), 20 green (RGB: 20, 100, 40), 20 blue (RGB: 0, 0, 220) and 20 yellow (RGB: 200, 150, 0), presented against a black background. Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement (with the restriction that two items could not be within 30 pixels of each other). The location of item colors to grid locations was completely randomized. 
For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles. Participants were asked to collect all of the targets within a trial by using the mouse to click on each target. Clicking on a target caused it to disappear from the display. If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun. Participants completed 1 practice trial and 20 full-completed experimental trials.

In the conjunction foraging task, search displays were composed of both circles and squares. For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow. Targets were defined by conjunctions of color and shape (e.g., red squares and green circles, with red circles and green squares as distractors). The assignment of targets and distractors was counterbalanced across participants (was it?). The procedure was otherwise identical to the feature foraging task.

@@

Participants with accuracy more than 3 SD below the group mean were excluded from analyses. For RT analyses, trials with RTs less than 300ms or more than 3 SD about the participant’s mean were excluded.

Two measures of individual strategy use were used: 1) Optimal choices, defined as percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors. When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target color (i.e., the color chosen on trial N was different to the color chosen on trial N-1).

@@

Only completed, accurate trials were analyzed. RTs were defined across the entire trial (i.e., from the start of the trial until the final target was collected). The main measure of interest was average run length per trial. A run was defined as a succession of one or more of the same target type, which was followed and preceded by the other target or no target. The average run length was the average number of target selections in a run.
